Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-09-24 GWLDCII.tex
rephrase statement of lemma 4.6

\begin{lem}\label{lem n and n-1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}.
Then \hlfix{$I_n^{W}$}{Does $I_n^W$ actually yeild any of the $+$s in $I_n^V$?}\note{I don't remember, but the point is that this is a two way statement, $I_n^W$ nd $I_{n-1}^W$ yield \emph{exacly} the plusses yielded by $I_n^{V}$, and it doesn't really matter which come from $I_n^W$ and which from $I_{n-1}^W$} and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
\end{lem}

>>>>

\begin{lem}\label{lem n and n-1}
Let $V$ and $W$ be as in Lemma~\ref{lem I}.
Then
  %$I_n^{W}$
  %and $I_{n-1}^{W}$ together yield the same plusses as $I_n^{V}$ did, along with two extra plusses which appear in the leftmost two boxes of the bottom row of the Le diagram of $W$.
%
%  Specifically,
  $I_n^W$ yields an $(n-3)\rightarrow n$ plus and $I_{n-1}^W$ yields an $(n-3)\rightarrow (n-1)$ plus along with any plusses yielded by $I_n^V$.
\end{lem}
